---
title: "Alcohol vs Seat choice"
author: "Alfredo Acevedo"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
   
  More students sit in the back seat are more likely have consumed alcohol, then how most do in the middle or front seat. It also shows how much is consumed.    
    
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
  
   The numerical graph shows how many times the class drinks a week and where they sit in the classroom. shows the front having only an average of in between one or two drinks. The ones who sit in the middle drinking an average of three to four drinks. and the average number of drinks for someone who sits in the back is about eight to nine drinks.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
This is the graph that shows the significant results.  

```{r}
plot(TukeyHSD(model1))
```
  
  This graph shows the difference between how much someone are drinking in the front, back, and the middle. It shows the difference between the front to back, middle to back, and finally middle to dront. It shows that there many people who sit in the back drink more then anyone that sits anywhere else. Also Middle and front show almost no difference.
   
## Conclusions


